Seagrass mapping and monitoring \\ along the coasts of Crete, Greece

### 2011-02-05 MScDiplom_Lemenkova.tex
comment 3rd of Valentijn: updated 'Figure 1.8 UML diagram'; changed document text font: Times

\documentclass[11pt]{article}
\special{papersize=140mm,210mm}
\usepackage{authblk}
%\usepackage{authorindex}
\usepackage{color}
\usepackage[stable]{footmisc }
\usepackage{setspace}
\usepackage[printonlyused,withpage]{acronym}
\usepackage[left=30mm,right=20mm,top=30mm,bottom=35mm]{geometry}
%\usepackage{glossary}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage[numbers]{natbib}
\usepackage{calc}
\usepackage{amsmath}
\usepackage{longtable}
\usepackage[svgnames,table]{xcolor}
\usepackage[subfigure]{tocloft}
%\usepackage[table]{xcolor}
\usepackage{paralist}
%\usepackage{makeidx}\makeindex
%\usepackage[makeindex,protected]{splitidx}
%\usepackage{index}
\usepackage{imakeidx}
\makeindex[name=concepts,title=Index of Concepts,intoc]
\makeindex[name=people,title=Index of People,intoc,columns=3,columnseprule]
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{fancyheadings}
\topmargin = 1pt
\headheight=10mm
\headsep=7pt
%\ensuremath
\usepackage{lastpage}
\usepackage{float}
\usepackage{subfig}
\usepackage{caption}
\usepackage{chngcntr}
\counterwithin{figure}{section}
\counterwithin{table}{section}
\usepackage{appendix}
\captionsetup{margin=10pt,font=small,labelfont=bf}
\usepackage{wrapfig}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\setcounter{tocdepth}{4}
\parindent 0pt
%\floatstyle{boxed} 
\restylefloat{figure}
\usepackage{hyperref}
\hypersetup{pdftitle={Seagrass mapping and monitoring along the coasts of Crete, Greece}, pdfauthor={Lemenkova Polina}, pdfsubject={MScThesis}, pdfcreator={Lemenkova Polina}, pdfproducer={Lemenkova Polina}, colorlinks=true,linkcolor=Navy, citecolor=Crimson, filecolor=magenta, urlcolor=blue}

@@

\begin{document}
\pagenumbering{roman}

@@

\section*{Document Outline}
	\markright{Structure of the MSc Thesis}
	\addcontentsline{toc}{section}{Document Outline}
\textit{Chapter 1}: \nameref{sec:1} is an introductory section. It describes general background of the research problem, outlines the need and actuality of the problem (including the environmental vulnerability of the seagrasses), and highlights limitations and possibilities of the remote sensing application for the current work. In this chapter we also set up research objectives, put research questions for hypothesis testing and sketch research approach for the proposed work.
\newline
In \textit{Chapter 2}: \nameref{sec:2} we review the existing literature and reported research experience on the similar problem: studies of spectral separability of various seafloor types, limitations and advantages of the remote sensing techniques applied for seagrass mapping seagrass ecology and mapping seagrass environment. We considered not only the Mediterranean environment, but also papers from Australian and Chinese scientists, because seagrass monitoring is most actively developed in the southern regions of our planet. The review of the existing RTM algorithms for the retrieval of the optical parameters, as well as description of various tools for the spectrometric measurements - are given in the same Chapter as well. More close attention has been given to the imaging hyperspectral radiometer Trios RAMSES, used for the data collection.\\
\textit{Chapter 3}: \nameref{sec:3} deals with the methods and materials used in current work. We start our discussion from the fieldwork area location and describe tools and instruments used during the fieldwork, as well as sampling design. Procedures of the data pre-processing and capturing imagery from the Google Earth are also presented in the same chapter. \\
\textit{Chapter 4}: \nameref{sec:4} presents to the reader the main results of the current MSc work, obtained during the processing fieldwork and other collected data. It starts from the review of the collected data from different sources, then describes the modelling component of the research, namely \ac{WASI} colour simulation and plotted resulting graphs. We also discuss here the particularities of various sensors, suitable enough for deriving radiometric information to discriminate sand from the seagrass. Furthermore, this chapter includes analysis of the spectral signatures of various seafloor cover types in conditions of changing environment, possibility and limitations for \textit{P.oceanica} spectral discrimination, statistical analysis of the data sets and mapping based on images processing.\\
\textit{Chapter 5}: \nameref{sec:5} summarizes and briefly discusses again the main results, reported in detail in a previous chapter. This chapter proposes some final discussions to the reader, and comes to the main research outcomes.\\
Finally, we suggest some recommendations for any further research focusing on the seagrass environment along the coasts of Crete (or other Mediterranean areas) in the final \nameref{sec:6}.\\
A lot of plotted graphs, statistical outcomes, tables, auxiliary (yet relevant to our research) pictures and images, illustrating our work - are collected in the \nameref{app}. Due to the standard editorial limitations of the current MSc work, it was not possible to include all them to the main chapters. However, we tried to make the structure of the Appendices most clear and easy-readable as possible, by dividing the Appendices into 10 various sub-sections and referencing to them from the main text where necessary. \\
The \nameref{bib} section includes literature and internet resources used for the current work. The cross-referencing and web hyper-referencing are used in the whole document to make reading more quick, effective and informative.\\
An Index is placed in the end of the Document to help the reader find what he is looking for.

>>>>

\documentclass[11pt]{article}
\special{papersize=140mm,210mm}
\usepackage{authblk}
%\usepackage{authorindex}
\usepackage{color}
\usepackage[stable]{footmisc }
\usepackage{setspace}
\usepackage[printonlyused,withpage]{acronym}
\usepackage[left=30mm,right=20mm,top=30mm,bottom=35mm]{geometry}
\usepackage{pslatex}
%\usepackage{times}
%\usepackage{psnfss}
%\usepackage{glossary}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage[numbers]{natbib}
\usepackage{calc}
\usepackage{amsmath}
\usepackage{longtable}
\usepackage[svgnames,table]{xcolor}
\usepackage[subfigure]{tocloft}
%\usepackage[table]{xcolor}
\usepackage{paralist}
%\usepackage{makeidx}\makeindex
%\usepackage[makeindex,protected]{splitidx}
%\usepackage{index}
\usepackage{imakeidx}
\makeindex[name=concepts,title=Index of Concepts,intoc]
\makeindex[name=people,title=Index of People,intoc,columns=3,columnseprule]
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{fancyheadings}
\topmargin = 1pt
\headheight=10mm
\headsep=7pt
%\ensuremath
\usepackage{lastpage}
\usepackage{float}
\usepackage{subfig}
\usepackage{caption}
\usepackage{chngcntr}
\counterwithin{figure}{section}
\counterwithin{table}{section}
\usepackage{appendix}
\captionsetup{margin=10pt,font=small,labelfont=bf}
\usepackage{wrapfig}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\setcounter{tocdepth}{4}
\parindent 0pt
%\floatstyle{boxed} 
\restylefloat{figure}
\usepackage{hyperref}
\hypersetup{pdftitle={Seagrass mapping and monitoring along the coasts of Crete, Greece}, pdfauthor={Lemenkova Polina}, pdfsubject={MScThesis}, pdfcreator={Lemenkova Polina}, pdfproducer={Lemenkova Polina}, colorlinks=true,linkcolor=Navy, citecolor=Crimson, filecolor=magenta, urlcolor=blue}

@@

\begin{document}
%\usefont{T1}
\pagenumbering{roman}

@@

\section*{Document Outline}
	\markright{Structure of the MSc Thesis}
	\addcontentsline{toc}{section}{Document Outline}
\textit{Chapter 1}: \nameref{sec:1} is an introductory section. It describes general background of the research problem, outlines the need and actuality of the problem (including the environmental vulnerability of the seagrasses), and highlights limitations and possibilities of the remote sensing application for the current work. In this chapter we also set up research objectives, put research questions for hypothesis testing and sketch research approach for the proposed work.
In \textit{Chapter 2}: \nameref{sec:2} we review the existing literature and reported research experience on the similar problem: studies of spectral separability of various seafloor types, limitations and advantages of the remote sensing techniques applied for seagrass mapping seagrass ecology and mapping seagrass environment. We considered not only the Mediterranean environment, but also papers from Australian and Chinese scientists, because seagrass monitoring is most actively developed in the southern regions of our planet. The review of the existing RTM algorithms for the retrieval of the optical parameters, as well as description of various tools for the spectrometric measurements - are given in the same Chapter as well. More close attention has been given to the imaging hyperspectral radiometer Trios RAMSES, used for the data collection.\\
\textit{Chapter 3}: \nameref{sec:3} deals with the methods and materials used in current work. We start our discussion from the fieldwork area location and describe tools and instruments used during the fieldwork, as well as sampling design. Procedures of the data pre-processing and capturing imagery from the Google Earth are also presented in the same chapter. \\
\textit{Chapter 4}: \nameref{sec:4} presents to the reader the main results of the current MSc work, obtained during the processing fieldwork and other collected data. It starts from the review of the collected data from different sources, then describes the modelling component of the research, namely \ac{WASI} colour simulation and plotted resulting graphs. We also discuss here the particularities of various sensors, suitable enough for deriving radiometric information to discriminate sand from the seagrass. Furthermore, this chapter includes analysis of the spectral signatures of various seafloor cover types in conditions of changing environment, possibility and limitations for \textit{P.oceanica} spectral discrimination, statistical analysis of the data sets and mapping based on images processing.\\
\textit{Chapter 5}: \nameref{sec:5} summarizes and briefly discusses again the main results, reported in detail in a previous chapter. This chapter proposes some final discussions to the reader, and comes to the main research outcomes.\\
Finally, we suggest some recommendations for any further research focusing on the seagrass environment along the coasts of Crete (or other Mediterranean areas) in the final \nameref{sec:6}.\\
A lot of plotted graphs, statistical outcomes, tables, auxiliary (yet relevant to our research) pictures and images, illustrating our work - are collected in the \nameref{app}. Due to the standard editorial limitations of the current MSc work, it was not possible to include all them to the main chapters. However, we tried to make the structure of the Appendices most clear and easy-readable as possible, by dividing the Appendices into 10 various sub-sections and referencing to them from the main text where necessary. \\
The \nameref{bib} section includes literature and internet resources used for the current work. The cross-referencing and web hyper-referencing are used in the whole document to make reading more quick, effective and informative.\\
All persons mentioned in the current document are listed in the Index of People. \\
An Index of Concepts is placed in the end of the Document to help the reader find what he is looking for.
